---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ieeecomtrade

This is a package to help you work with IEEE COMTRADE files. Currently, this package is restricted to:

- COMTRADE 1999 format
- considers only configuration and data files
- data files must be ASCII

In time, it is hoped to lift these restrictions, particularly as the need may present itself.

## Installation

This package is not yet on CRAN. However, you can install it from GitHub:

```{r, eval=FALSE}
# install.packages("devtools")
install_github("ijlyttle/ieeecomtrade")
```

## Usage

The central object in this package is a **comtrade** object. You can build a comtrade object by reading in the configuration and data files, or you can read a zip file that contains exactly one configuration file and exactly one data file.

Let's look at reading in some sample files provided with this package. As a first example, let's build a comtrade object by reading the configuration file and data file individually.

```{r}
library("ieeecomtrade")

config <- 
  ct_example("keating_1999.CFG") %>%  # returns a file path
  ct_read_config()                    # returns a configuration object

data <- 
  ct_example("keating_1999.DAT") %>%
  ct_read_data_config(config)
  
keating <- comtrade(config = config, data = data)  
```
Similarly, you can read from a zip file

```{r}
keating <- 
  ct_example("keating_1999.zip") %>%
  ct_read_zip()
```

If you want a data frame with scaled values and a timestamp:

```{r}
ct_instant(keating)
```

## Code if Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
